The ChEMBL database as Linked Open Data

### 2012-11-20 article.tex
Applied the linguistic suggestion

Taking these points into account, we believe that the adoption of RDF and community based ontologies allows
novel use cases to be solved using the ChEMBL data that would not otherwise be achievable. More importantly, the adoption of explicit
semantics simplifies integration with other resources, as others can more easily understand the intent and purpose of each part of the ChEMBL dataset.
This is a requirement which is essential to the efforts of cheminformatics researchers wishing to infer knowledge
from ChEMBL as well as other datasets.

>>>>

Taking these points into account, we believe that the adoption of RDF and community based ontologies allows
novel use cases to be addressed using the ChEMBL data that would not otherwise be achievable. More importantly, the adoption of explicit
semantics simplifies integration with other resources, as others can more easily understand the intent and purpose of each part of the ChEMBL dataset.
This is a requirement which is essential to the efforts of cheminformatics researchers wishing to infer knowledge
from ChEMBL as well as other datasets.
